---
title: 'Decarbonization Project Assignment, Part 1'
author: "Gerald Nelson Jr."
date: "Due Oct. 30, 2017"
bibliography: "decarbonization.bib" # this line tells RMarkdown which file to use for the bibliography
output: 
  html_document: default
  pdf_document:
    include:
      in_header: "ees3310.sty" # This line just tells RMarkdown to use a style file to format the PDF file with Times Roman font.
---
```{r setup, include=FALSE}
knitr::knit_hooks$set(inline = function(x) { knitr:::format_sci(x, 'md')})
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)

# This section loads necessary R libraries and sources scripts that define 
# useful functions format_md.
# 
data_dir = "data"
script_dir = "scripts"

if (!dir.exists('data')) dir.create('data')

library(pacman)

# Some lab computers fail to load tidyverse
# because bindr is not installed.
# This will prevent such errors.
if (!p_isinstalled(bindr)) p_install(bindr)


# Load all of the following packages.
# Install any missing packages.


# This sets the default style for ggplot
theme_set(theme_bw(base_size = 15))

# Load basic utility scripts
source('scripts/utils.R', chdir = T)

```

```{r launch_kaya_tool}
library (pacman)
p_load_gh ("gilligan-ees-3310/kayatool")


```
#Introduction

In this paper, we will examine the Kaya variable trends over time for United States, japan and then the japan as a whole. Then, we will examine the decarbonization rates necessary to reach the emissions reduction target set for each country and the japan. This paper will conclude with a discussion of the implications drawn from the results of these models.


#Data and Plots

**First, Let's look at the kaya variable data tables and plot trends for the United States.**

```{r load_japan}
japan_data = read_csv('japan.csv')
```

```{r japan_kaya_identity_values_constants}
japan_P = filter(japan_data, year == 2016)$P
japan_G =filter(japan_data, year == 2016)$G
japan_g = filter(japan_data, year == 2016)$g
japan_E = filter(japan_data, year == 2016)$E
japan_F = filter(japan_data, year == 2016)$F
japan_e = filter(japan_data, year == 2016)$e
japan_ef = filter(japan_data, year == 2016)$ef



japan_values = tibble(variable = c("P", "g", "e", "f"), 
               japan_value = c(japan_P, japan_g, japan_e, japan_f))

kable (japan_values)


```


```{r japan_kaya_rates_of_change}
japan_rate_P= -0.0014
japan_rate_g = 0.0121
japan_rate_e = -0.0273
japan_rate_f = -0.0170
japan_rate_ef = -.0103
japan_rate_G =-.0103
japan_rate_E = -.0166
japan_rate_F = -.0004

japan_rates = table(variable = c("P", "g", "e", "f"), 
               japan_rate = c(japan_rate_P, japan_rate_g, japan_rate_e, japan_rate_f))

kable (japan_rates)

```

```{r japan_kaya_rates_of_change}
japan_rate_e_new = japan_rate_F -(japan_rate_P + japan_rate_g)

```

```{r japan_growth_rate}

japan_P_2050 = (japan_P * exp(japan_rate_P*(2050-2010)))
japan_g_2050 = (japan_g * exp (japan_rate_g*(2050-2010)))

japan_f_2050 = (japan_f * exp (japan_rate_f * (2050-2010)))
japan_ef_2050 = (japan_ef * exp (japan_rate_ef * (2050-2010)))
japan_F_2050 = (japan_F * exp (japan_rate_F * (2050-2010)))
japan_e_2050 = (japan_e*(exp (japan_rate_e * (2050-2010))))



japan_e_2050
japan_ef_2050
japan_e_2050
japan_f_2050
japan_g_2050
japan_P_2050

japan_2050_values = tibble(variable = c("P", "g", "e", "f"), 
               japan_2050_value = c(japan_P_2050, japan_g_2050, japan_e_2050, japan_f_2050))

kable (japan_2050_values)

```

```{r japan_F_2005}

japan_F_2010 = 1191
japan_e_2010 = 3.45


```

```{r japan_F_target}

japan_F_target = japan_F *(1-.66)
japan_F_target

japan_implied_rate_F = log(japan_F_2050/ japan_F_2005) / (2050 - 2005)

japan_implied_rate_F

japan_implied_rate_ef = japan_rate_F _ (japan_rate_P + japan_rate_g)

japan_implied_rate_e = log(japan_e_2050/ japan_e_2010) / (2050 - 2010)

japan_implied_rate_f = japan_implied_rate_e - japan_implied_rate_e

```



```{r japan_implied_rate_F}

japan_implied_rate_F = log(japan_F_2050/ japan_F_2005) / (2050 - 2005)

japan_implied_rate_F
```

```{r japan_decarbonization_rate}
japan_decarbonization_rate = japan_implied_rate_F -japan_rate_P - japan_rate_g

japan_decarbonization_rate


```


```{r load_japan}
japan_data = read_csv('japan.csv')
```


```{r plot_japan_g}
ggplot(japan_data, aes(x = year, y= g)) +
  geom_line() + geom_point()
```

```{r plot_japan_e}
ggplot(japan_data, aes(x = year, y= e)) +
  geom_line() + geom_point()
```

```{r plot_japan_f}
ggplot(japan_data, aes(x = year, y= f)) +
  geom_line() + geom_point()
```

```{r plot_japan_log_P}
ggplot(japan_data, aes(x = year, y= P)) +
  geom_line() + geom_point() +
  scale_y_log10()
```

```{r plot_japan_log_g}
ggplot(japan_data, aes(x = year, y= g)) +
  geom_line() + geom_point() +
  scale_y_log10()
```

```{r plot_japan_log_e}
ggplot(japan_data, aes(x = year, y= e)) +
  geom_line() + geom_point() +
  scale_y_log10()
```

```{r plot_japan_log_f}
ggplot(japan_data, aes(x = year, y= f)) +
  geom_line() + geom_point() + 
  scale_y_log10()
```


```{r japan_calculate_slopes}
# average annual growth rate of per-capita GDP, in percent per year
P_fit = lm(log(P)~ year, data = japan_data)
rate_P = summary(P_fit)$coefficients['year', 'Estimate']

g_fit = lm(log(g)~ year, data = japan_data)
rate_g = summary(g_fit)$coefficients['year', 'Estimate']

e_fit = lm(log(e)~ year, data = japan_data)
rate_e = summary(e_fit)$coefficients['year', 'Estimate']




```
 
 
---decarbonization part 2 top down
```{r load_japan_data}
target_year = 2050
reference_year = 2010
start_year = 2016

target_japan_reduction = 0.66

japan_data = get_kaya_data("japan")
japan_fuel_mix = get_fuel_mix("japan") %>% arrange(fuel)
japan_projection = project_top_down("japan", target_year)

target_japan_emissions = filter(japan_data, year == reference_year)$F * (1 - target_japan_reduction)
projected_japan_E = japan_projection$E
```


```{r top_down}
target_japan_reduction = 0.66
japan_data = get_kaya_data("japan")
japan_fuel_mix = get_fuel_mix("japan") %>% arrange(fuel)
japan_projection = project_top_down("japan", target_year) #What does this mean?
target_japan_emissions = filter(japan_data, year == reference_year)$F * (1 - target_japan_reduction)
projected_japan_E = japan_projection$E
```

```{r emissions factors}
e_factors = emissions_factors()
plot_fuel_mix(japan_fuel_mix)
```


```{r fuel mix}

kable(e_factors)

```

```{r next top down}

